Title

### 2023-03-30 Cosas-Escritas-Antes.tex
Cap2 y puntos cap5

\textbf{Property 1:} \textit{An $n$-qubit OPR circuit can always be transformed into the form of circuit \ref{fig: OPR general}, where $A$ and $B$ are $n$-qubit gates that don't depend on the parameter
and $s = s(p)$ is a function of the parameter.}\\

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate[wires = 4,nwires=3]{B} & \ctrl{3} & \qw & \gate[wires=4,nwires=3]{A} & \qw \\
\lstick{$q_1$} & \qw &  & \ctrl{2} & \qw & & \qw \\
\vdots & \vdots & & & \vdots & \\
\lstick{$q_{n-1}$} & \qw & & \gate{R_{\sigma_3}(2s(p))} & \qw & & \qw
\end{quantikz}
\caption{Forma general de un circuito RP.}
\label{fig: OPR general}
\end{figure}

@@

Therfore, an OPR circuit can be transformed in a way that the rotation is around $\sigma_3$ and applied on the last qubit 
(possibly controlled by other qubits), 
so that it has the form \ref{fig: OPR general}. $\blacksquare$ \\ \\

@@

\textbf{Proof:} Because of property 1, we know that any OPR
circuit can be converted into the form \ref{fig: OPR general},
so that we only need to consider the operator for that circuit. 
The $j$-th column of the circuit's matrix will be the result of applying the 
circuit to the state $|j\rangle$. 
First, applying $B$ to that state results in $B_{0,j} |0\rangle |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
 which can be rewritten by separating the states to which the controlled 
rotation will be applied from those to which it won't as follows:
\begin{eqnarray}
\sum_{k \in Ctrl} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
where $Ctrl$ is the set of all basis states of the first $n-1$ qubits
such that they fulfill the controls of the rotation gate and therefore the gate is applied.

@@

The circuit that does this is presented in figure \ref{fig: circuito}, where $|\vec{\gamma}\rangle$ is defined as the $2n$ qubits state $|\vec{\gamma} \rangle = \otimes_{i=0}^n |\gamma_i \; \text{in binary} \rangle$. For example, if $\vec{\gamma} = (0,3,1,\cdots)$, then this state is defined as $|\vec{\gamma} \rangle = |001101 \rangle$.

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2n$ qubits state $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2n-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2n-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{Circuit for a n-qubit Pauli channel.}
\label{fig: circuito}
\end{figure}

@@

Dynamical maps can be implemented using the same method as in figure \ref{fig: circuito}, with the only difference that now the state to be created on the ancilla qubits depends on parameter $p$ and it is given by $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}(p)} |\vec{\gamma}\rangle$.  \\

@@

For the special case of a system consisting of only one qubit, a Pauli channel takes the form
\begin{eqnarray}
\varepsilon(\rho) = k_0 I \rho I + k_1 X \rho X + k_2 Y \rho Y + k_3 Z \rho Z,
\end{eqnarray}
and the circuit that can be used to implement it reduces to:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$\sqrt{k_0} |0 \rangle |0 \rangle + \sqrt{k_1} |0 \rangle |1 \rangle + \sqrt{k_2} |1 \rangle |0 \rangle + \sqrt{k_3} |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{ Circuit for a one qubit Pauli channel.}
\label{fig: canal-1qbit} 
\end{figure}

@@

To implement this dynamical map using the circuit presented in figure \ref{fig: one-rot}, it is necessary to create the state
\begin{eqnarray}
\left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right)
\end{eqnarray}
on the $2$ ancilla qubits. Luckily, this state can be written in the form $\vec{c} + \vec{a} \cos s + \vec{b} \sin s$ as
\begin{eqnarray}
\begin{pmatrix}
1/2 \\
0 \\ 
0 \\
1/2
\end{pmatrix} + \begin{pmatrix}
0 \\
1/2 \\
1/2 \\
0
\end{pmatrix}  \cos s + \begin{pmatrix}
-1/2 \\
0 \\
0 \\
1/2
\end{pmatrix} \sin s
\end{eqnarray}
with $s = \arcsin p$. According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation. The circuit used will have the same form as that in figure \ref{fig: canal-1qbit}, where the part used to create the state on the ancilla qubits will be:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$aq_0$} & \gate[wires=2]{B} & \ctrl{1} & \gate[wires=2]{A} & \qw \\
\lstick{$aq_{1}$} & & \gate{R_{\sigma_2}(2s)} & & \qw  \\
\end{quantikz}
\caption{Circuit to create 2-qubit state}
\end{figure}

@@

\textbf{Example:} Consider $H = \sigma_3 \otimes \sigma_2$ for two qubits. In this case, the hamiltonian matrix is
\begin{eqnarray}
H = \begin{pmatrix}
0 & -i & 0 & 0 \\
i & 0 & 0 & 0 \\
0 &0 & 0 & i \\
0 & 0 & -i & 0
\end{pmatrix}
\end{eqnarray}
that has eigenvalues $\{-1,-1,1,1\}$. This matrix can be diagonalized as
\begin{eqnarray}
Q \begin{pmatrix}
-1 & 0 &0 & 0 \\
0 & -1 &0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix} Q^{\dagger} \;\; ,\;\; Q:= \begin{pmatrix}
-\sqrt{2}/2 & 0 & 0 & - \sqrt{2}/2 \\
\sqrt{2}/2 i & 0 & 0 & -\sqrt{2}/2 i \\
0 &-\sqrt{2}/2 & \sqrt{2}/2 & 0\\
0 &-\sqrt{2}/2 i & -\sqrt{2}/2i & 0
\end{pmatrix},
\end{eqnarray}
therefore, the exponential matrix is given by:
\begin{eqnarray}
U = e^{iHt} = Q \begin{pmatrix}
e^{-it} & 0 &0 & 0 \\
0 & e^{-it} &0 & 0 \\
0 & 0 & e^{it} & 0 \\
0 & 0 & 0 & e^{it}
\end{pmatrix} Q^{\dagger}
\end{eqnarray}
The diagonal matrix between $Q$ and $Q^{\dagger}$ is simply $R_{\sigma_3} (2s)$ applied to the first qubit and without control qubits, therefore
the OPR circuit for this operation is given by figure \ref{fig: 2x3}

\begin{figure}
\centering
\begin{quantikz}
\lstick{$q_0$} & \gate[wires=2]{Q^{\dagger}} & \swap{1} & \qw & \swap{1} & \gate[wires=2]{Q} & \qw \\
\lstick{$q_1$} & \qw & \targX{} & \gate{R_Z(2t)} & \targX{}  & \qw & \qw\\
\end{quantikz}
\caption{Circuito para $\sigma_2 \oplus \sigma_3$}
\label{fig: 2x3}
\end{figure}
I tried out this circuit on 
real quantum computers for values of $t$ between 
$0$ and $\pi$ and after applying QPT consistently got a fidelity of around $0.85$ for 
every value of $t$.\\

@@

\end{document}

>>>>

\textbf{Property 1:} \textit{An $n$-qubit OPR circuit can always be transformed into the form of circuit \ref{fig: OPR general-A}, where $A$ and $B$ are $n$-qubit gates that don't depend on the parameter
and $s = s(p)$ is a function of the parameter.}\\

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate[wires = 4,nwires=3]{B} & \ctrl{3} & \qw & \gate[wires=4,nwires=3]{A} & \qw \\
\lstick{$q_1$} & \qw &  & \ctrl{2} & \qw & & \qw \\
\vdots & \vdots & & & \vdots & \\
\lstick{$q_{n-1}$} & \qw & & \gate{R_{\sigma_3}(2s(p))} & \qw & & \qw
\end{quantikz}
\caption{Forma general de un circuito RP.}
\label{fig: OPR general-A}
\end{figure}

@@

Therfore, an OPR circuit can be transformed in a way that the rotation is around $\sigma_3$ and applied on the last qubit 
(possibly controlled by other qubits), 
so that it has the form \ref{fig: OPR general-A}. $\blacksquare$ \\ \\

@@

\textbf{Proof:} Because of property 1, we know that any OPR
circuit can be converted into the form \ref{fig: OPR general-A},
so that we only need to consider the operator for that circuit. 
The $j$-th column of the circuit's matrix will be the result of applying the 
circuit to the state $|j\rangle$. 
First, applying $B$ to that state results in $B_{0,j} |0\rangle |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
 which can be rewritten by separating the states to which the controlled 
rotation will be applied from those to which it won't as follows:
\begin{eqnarray}
\sum_{k \in Ctrl} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
where $Ctrl$ is the set of all basis states of the first $n-1$ qubits
such that they fulfill the controls of the rotation gate and therefore the gate is applied.

@@

The circuit that does this is presented in figure \ref{fig: circuito-A}, where $|\vec{\gamma}\rangle$ is defined as the $2n$ qubits state $|\vec{\gamma} \rangle = \otimes_{i=0}^n |\gamma_i \; \text{in binary} \rangle$. For example, if $\vec{\gamma} = (0,3,1,\cdots)$, then this state is defined as $|\vec{\gamma} \rangle = |001101 \rangle$.

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2n$ qubits state $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2n-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2n-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{Circuit for a n-qubit Pauli channel.}
\label{fig: circuito-A}
\end{figure}

@@

Dynamical maps can be implemented using the same method as in figure \ref{fig: circuito-A}, with the only difference that now the state to be created on the ancilla qubits depends on parameter $p$ and it is given by $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}(p)} |\vec{\gamma}\rangle$.  \\

@@

For the special case of a system consisting of only one qubit, a Pauli channel takes the form
\begin{eqnarray}
\varepsilon(\rho) = k_0 I \rho I + k_1 X \rho X + k_2 Y \rho Y + k_3 Z \rho Z,
\end{eqnarray}
and the circuit that can be used to implement it reduces to:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$\sqrt{k_0} |0 \rangle |0 \rangle + \sqrt{k_1} |0 \rangle |1 \rangle + \sqrt{k_2} |1 \rangle |0 \rangle + \sqrt{k_3} |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{ Circuit for a one qubit Pauli channel.}
\label{fig: canal-1qbit-A} 
\end{figure}

@@

To implement this dynamical map using the circuit presented in figure \ref{fig: one-rot-A}, it is necessary to create the state
\begin{eqnarray}
\left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right)
\end{eqnarray}
on the $2$ ancilla qubits. Luckily, this state can be written in the form $\vec{c} + \vec{a} \cos s + \vec{b} \sin s$ as
\begin{eqnarray}
\begin{pmatrix}
1/2 \\
0 \\ 
0 \\
1/2
\end{pmatrix} + \begin{pmatrix}
0 \\
1/2 \\
1/2 \\
0
\end{pmatrix}  \cos s + \begin{pmatrix}
-1/2 \\
0 \\
0 \\
1/2
\end{pmatrix} \sin s
\end{eqnarray}
with $s = \arcsin p$. According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation. The circuit used will have the same form as that in figure \ref{fig: canal-1qbit-A}, where the part used to create the state on the ancilla qubits will be:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$aq_0$} & \gate[wires=2]{B} & \ctrl{1} & \gate[wires=2]{A} & \qw \\
\lstick{$aq_{1}$} & & \gate{R_{\sigma_2}(2s)} & & \qw  \\
\end{quantikz}
\caption{Circuit to create 2-qubit state}
\end{figure}

@@

\textbf{Example:} Consider $H = \sigma_3 \otimes \sigma_2$ for two qubits. In this case, the hamiltonian matrix is
\begin{eqnarray}
H = \begin{pmatrix}
0 & -i & 0 & 0 \\
i & 0 & 0 & 0 \\
0 &0 & 0 & i \\
0 & 0 & -i & 0
\end{pmatrix}
\end{eqnarray}
that has eigenvalues $\{-1,-1,1,1\}$. This matrix can be diagonalized as
\begin{eqnarray}
Q \begin{pmatrix}
-1 & 0 &0 & 0 \\
0 & -1 &0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix} Q^{\dagger} \;\; ,\;\; Q:= \begin{pmatrix}
-\sqrt{2}/2 & 0 & 0 & - \sqrt{2}/2 \\
\sqrt{2}/2 i & 0 & 0 & -\sqrt{2}/2 i \\
0 &-\sqrt{2}/2 & \sqrt{2}/2 & 0\\
0 &-\sqrt{2}/2 i & -\sqrt{2}/2i & 0
\end{pmatrix},
\end{eqnarray}
therefore, the exponential matrix is given by:
\begin{eqnarray}
U = e^{iHt} = Q \begin{pmatrix}
e^{-it} & 0 &0 & 0 \\
0 & e^{-it} &0 & 0 \\
0 & 0 & e^{it} & 0 \\
0 & 0 & 0 & e^{it}
\end{pmatrix} Q^{\dagger}
\end{eqnarray}
The diagonal matrix between $Q$ and $Q^{\dagger}$ is simply $R_{\sigma_3} (2s)$ applied to the first qubit and without control qubits, therefore
the OPR circuit for this operation is given by figure \ref{fig: 2x3-A}

\begin{figure}
\centering
\begin{quantikz}
\lstick{$q_0$} & \gate[wires=2]{Q^{\dagger}} & \swap{1} & \qw & \swap{1} & \gate[wires=2]{Q} & \qw \\
\lstick{$q_1$} & \qw & \targX{} & \gate{R_Z(2t)} & \targX{}  & \qw & \qw\\
\end{quantikz}
\caption{Circuito para $\sigma_2 \oplus \sigma_3$}
\label{fig: 2x3-A}
\end{figure}
I tried out this circuit on 
real quantum computers for values of $t$ between 
$0$ and $\pi$ and after applying QPT consistently got a fidelity of around $0.85$ for 
every value of $t$.\\

@@
